Hypertension statistics for US adults: an open-source web application for analysis and visualization of US NHANES data

### 2024-02-09 paper/manuscript.Rmd
finalized changes for pub, committed long after they were made

```{r, fig.height=3.75}

@@

```{r, fig.height=3.75}

@@

@@

A. Among non-pregnant US adults with hypertension `r single_par`
```{r, fig.height=3.75}

@@

B. Among non-pregnant US adults who self-report taking antihypertensive medication `r single_par`
```{r, fig.height=3.75}
fig_print(fig_main_4_b)
```
Age adjustment was performed through direct standardization, using the estimated age distribution of US adults with hypertension from 1999 to 2020 as the standard (26.4%, 43.4%, 17.0% and 13.2% being 18 to 44 years, 45 to 64, 65 to 74, and ≥ 75 years of age, respectively) `r single_par`

>>>>

```{r fig_1, fig.height=3.75}

@@

```{r fig_2, fig.height=3.75}

@@

```{r fig_3}

@@

A. Among non-pregnant US adults with hypertension `r single_par`
```{r fig_4a, fig.height=3.75}

@@

B. Among non-pregnant US adults who self-report taking antihypertensive medication `r single_par`
```{r fig_4b, fig.height=3.75}
fig_print(fig_main_4_b)
```
Age adjustment was performed through direct standardization, using the estimated age distribution of US adults with hypertension from 1999 to 2020 as the standard (26.4%, 43.4%, 17.0% and 13.2% being 18 to 44 years, 45 to 64, 65 to 74, and ≥ 75 years of age, respectively) `r single_par`
